\section{Introduction}

The integration of artificial intelligence with robotics has opened new frontiers in human-robot interaction (HRI). As robots become increasingly autonomous and deployed in complex real-world environments, the need for transparent and interpretable decision-making becomes paramount.
This project addresses the challenge of making robotic systems more explainable by leveraging Large Language Models (LLMs) to translate low-level sensor data and perception information into natural language explanations.

\subsection{Problem statement}

Modern robots operate using complex algorithms that process vast amounts of sensor data to make navigation and behavioral decisions.
However, these decisions often remain opaque to human users, creating a barrier to trust and effective collaboration.
The challenge lies in bridging the gap between machine perception and human understanding.

The primary goal is to develop an AI-powered robot capable of evaluating its past decisions, particularly when revisiting locations.
For example, the robot should be able to explain: "I recognize this area—I previously visited it on [date/time] and made a certain decision."
If the environment has changed since the last visit, the robot should update its reasoning to reflect the new context, rather than relying solely on prior experiences.

\subsection{Objectives}

This project aims to:
\begin{itemize}
    \item Design a framework for integrating LLMs with robotic perception systems
    \item Develop a prototype system that can explain robot path decisions in natural language
    \item Evaluate the effectiveness of LLM-generated explanations in enhancing human understanding
    \item Assess the impact on user trust and satisfaction in human-robot interactions
\end{itemize}
