\section{Conclusion}

\subsection{Summary of contributions}

This project successfully demonstrated the feasibility of using Large Language Models to enhance human-robot communication through natural language explanations of robotic decisions.
Key contributions include:

\begin{itemize}
    \item A novel integration framework for LLMs in robotic explanation systems
    \item A working prototype that translates low-level perception data into natural language (theoradicaly)
    \item Empirical evaluation demonstrating improved user understanding and engagement
    \item Open-source implementation available for further research and development
\end{itemize}

\subsection{Impact and implications}

The work addresses a critical gap in human-robot interaction by making robotic decision-making more transparent and interpretable.
This has implications for:
\begin{itemize}
    \item Increased user trust in autonomous systems
    \item Enhanced collaboration in human-robot teams
    \item Improved debugging and system maintenance
    \item Better user training and system adoption
\end{itemize}

\subsection{Future work}
Several directions for future research emerge from this work:
\begin{itemize}
    \item \textbf{Real-time integration :} Developing more efficient processing pipelines for live robot systems.
    \item \textbf{Multimodal explanations :} Incorporating visual and gestural explanation modalities.
    \item \textbf{Personalized explanations :} Adapting explanation style to individual user preferences.
    \item \textbf{Domain expansion :} Extending beyond path planning to other robotic decision domains.
    \item \textbf{Fine-tuning optimization :} We can develop robot-specific language models to improve performance, or we can directly train a robot to perform the exact task we are searching for.
\end{itemize}

\subsection{Final remarks}

The integration of Large Language Models with robotic systems represents a promising approach to bridging the communication gap between humans and machines. As LLM technology continues to advance, we can expect even more sophisticated and natural human-robot interactions, ultimately leading to more effective and trustworthy autonomous systems.
The open-source nature of this implementation encourages further research and development in this important area of human-robot interaction.
